On the formation of H$\alpha$ line emission around classical T Tauri stars: the disc-wind-magnetosphere hybrid model

### 2006-01-31 TTau_Halpha/submit/kurosawa.tex
Added "sumbit" directory containing the copy of kurosawa.tex and eps figures which renamed to fig01.eps, fig02.eps and etc.  RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@651 25464f21-6099-402c-b30a-640f1d40d38b

    \includegraphics[%
      scale=0.6]{figures/discwind.eps}

@@

    \begin{tabular}{cc}
      \includegraphics[%
	clip,
	scale=0.59]{plots/dw_vp_vphi.eps}~~~~~~&
      \includegraphics[%
	clip,
	scale=0.59]{plots/dw_rho.eps}\tabularnewline
    \end{tabular}

@@

    \includegraphics[%
      clip,
      scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}

@@

    \includegraphics[%
      clip,
      scale=0.59]{figures/broadening.eps}

@@

    \includegraphics[%
      clip,
      scale=0.59]{figures/acc_inc_effect.eps}

@@

    \includegraphics[%
      clip,
      scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45]{figures/discwind_d_effect.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45]{figures/discwind_mdot_effect.eps}

@@

    \includegraphics[%
      clip,
      scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45]{figures/discwind_mu_effect.eps}

@@

%    \includegraphics[%
%      clip,
%      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
    \includegraphics[%
	clip,
     scale=0.45, angle=270]{figures/discwind_hybrid_ha_image_grey.eps}

@@

    \includegraphics[%
      clip,
      scale=0.65]{figures/atlas_reipurth_like_discwind.eps}

@@

    \begin{tabular}{cc}
      \includegraphics[%
	clip,
	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}&
      \includegraphics[%
	clip,
	scale=0.61]{figures/stellarwind_inc_effect.eps}\tabularnewline
    \end{tabular}

@@

    \includegraphics[%
      scale=0.3]{figures/overview4.eps}

@@

  \begin{center}
      \includegraphics[%
	clip,
	scale=0.6]{figures/discwind_hybrid_mdot7_inc10.eps}\tabularnewline
      \vspace{0.5 cm}

      \includegraphics[%
	clip,
      scale=0.6]{figures/discwind_hybrid_mdot7_inc55.eps}\tabularnewline

@@

      \includegraphics[%
	clip, scale=0.6]{figures/discwind_hybrid_mdot7_inc80.eps}\tabularnewline
  \end{center}

@@

  \begin{center}
      \includegraphics[%
	clip,
	scale=0.6]{figures/discwind_hybrid_mdot8_inc10.eps}\tabularnewline
      \vspace{0.5 cm}

      \includegraphics[%
	clip,
      scale=0.6]{figures/discwind_hybrid_mdot8_inc55.eps}\tabularnewline

@@

      \includegraphics[%
	clip, scale=0.6]{figures/discwind_hybrid_mdot8_inc80.eps}\tabularnewline
  \end{center}

@@

  \begin{center}
      \includegraphics[%
	clip,
	scale=0.6]{figures/discwind_hybrid_mdot9_inc10.eps}\tabularnewline
      \vspace{0.5 cm}

      \includegraphics[%
	clip,
      scale=0.6]{figures/discwind_hybrid_mdot9_inc55.eps}\tabularnewline

@@

      \includegraphics[%
	clip, scale=0.6]{figures/discwind_hybrid_mdot9_inc80.eps}\tabularnewline
  \end{center}

>>>>

    \includegraphics[%
      scale=0.6]{fig01.eps}

@@

    \begin{tabular}{cc}
      \includegraphics[%
	clip,
	scale=0.59]{fig02a.eps}~~~~~~&
      \includegraphics[%
	clip,
	scale=0.59]{fig02b.eps}\tabularnewline
    \end{tabular}

@@

    \includegraphics[%
      clip,
      scale=0.45]{fig03.eps}

@@

    \includegraphics[%
      clip,
      scale=0.59]{fig04.eps}

@@

    \includegraphics[%
      clip,
      scale=0.59]{fig05.eps}

@@

    \includegraphics[%
      clip,
      scale=0.9]{fig06.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45]{fig07.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45]{fig08.eps}

@@

    \includegraphics[%
      clip,
      scale=0.9]{fig09.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45]{fig10.eps}

@@

    \includegraphics[%
      clip,
      scale=0.45,angle=270]{fig11.eps}
%    \includegraphics[%
%	clip,
%     scale=0.45, angle=270]{fig11_grey.eps}

@@

    \includegraphics[%
      clip,
      scale=0.65]{fig12.eps}

@@

    \begin{tabular}{cc}
      \includegraphics[%
	clip,
	scale=0.45]{fig13a.eps}&
      \includegraphics[%
	clip,
	scale=0.61]{fig13b.eps}\tabularnewline
    \end{tabular}

@@

    \includegraphics[%
      scale=0.3]{fig14.eps}

@@

  \begin{center}
      \includegraphics[%
	clip,
	scale=0.6]{fig_a1_01.eps}\tabularnewline
      \vspace{0.5 cm}

      \includegraphics[%
	clip,
      scale=0.6]{fig_a1_02.eps}\tabularnewline

@@

      \includegraphics[%
	clip, scale=0.6]{fig_a1_03.eps}\tabularnewline
  \end{center}

@@

  \begin{center}
      \includegraphics[%
	clip,
	scale=0.6]{fig_a2_01.eps}\tabularnewline
      \vspace{0.5 cm}

      \includegraphics[%
	clip,
      scale=0.6]{fig_a2_02.eps}\tabularnewline

@@

      \includegraphics[%
	clip, scale=0.6]{fig_a2_03.eps}\tabularnewline
  \end{center}

@@

  \begin{center}
      \includegraphics[%
	clip,
	scale=0.6]{fig_a3_01.eps}\tabularnewline
      \vspace{0.5 cm}

      \includegraphics[%
	clip,
      scale=0.6]{fig_a3_02.eps}\tabularnewline

@@

      \includegraphics[%
	clip, scale=0.6]{fig_a3_03.eps}\tabularnewline
  \end{center}
